---
output:
  word_document: default
  html_document: default
---
##431_HW3_QianCao
###3.15 Satisfaction with allocation of concert
a): Anecdotal Data: 3 Students could only represent individual cases.  
b): Sample Data: Students chose to provide opinios represent population of students who attended the concert  
c): Sample Data: Still represent population of students
d): Does not seem like an experiment: No, the survey measures the scales but not influence the response  
e): Anecdotal data here is mainly small indivuduals opinions but even presenting any general cases, but Sample data collects could be seen as representing the overall students, but the survey conducted is just a observation survey which does not influence the reponses at all 

###3.105 Two ways to ask sensative questions  
1): Use CASI method.   
Reason: Comparing to CAPI, CASI has lower response bais, because sunjects may tend to tell truth more likely in CAPI survey.  

###4.5 Winning at Craps  
Shooter wins at 7 or 11 Combinations are:  
For 7: c(1-6,2-5,3-4,6-1,5-2,4-3)  
For 11: c(5-6,6-5)  
While 2 dice have all combination is: 6*6=36  
Therefore probability that shooter wins immdiately is:   
8/36 =0.22222  

###4.34 PINs
a): Total 10^4=10,000 PINs possibilities exist   
b): probability at least having 1 zero stands for Complementry of P(none of 0 existing) = 1-  (9^4 / 10^4) = 0.3439  

###5. Letters and Envelopes  
**What is the probability that NONE of the letters arrive at the intended address?**  
P(1st envelop incorrect) = 2/3  
P(2nd envelop incorrect) = 1/2  
P(3rd envelop incorrect) = 1  
Therefore P(all are incorrect) = (2/3)* (1/2) * 1 = 1/3

###6. Powerball 
**Find the probability that a valid lottery ticket matches 3 out of 5 white balls and match the Powerball**  
```{r}
answer = (choose(5,3)*choose(64,2))/choose(69,5)
answer
```

###7. Baseball series
**What is the probability that the fifth game needs not be played to decide the winner?**  
 I. Avoid playing 5th game = 1 - P(playing 5th game)  
 II. P(playing 5th game) = first 4 games need to be 2:2  
 Therefore: P(avoid playing 5th game) = 
```{r}
P = 1-(choose(4,2)/(2^4))
P
```



