---
title: "431_HW7_QianCao"
output: word_document
---

### 7.81 Sales of small applicance across months
a) Using H-mstp-C-C procedure：7 steps
```{r}
m1=53
n1=60
var1=12^2
n2=58
m2=50
var2=10^2
M = m1-m2
df = min(n1,n2)-1
T= qt(c(0.025,0.975),df = df)
MOE = T[2]*sqrt(var1/n1+var2/n2)

CI_lhs = round(M - MOE,2)
CI_rhs = round(M + MOE,2)
```
95% CI interval for the difference in mean number of units sold is (`r CI_lhs` , `r CI_rhs`)   

b) We are 95% confident that mean of sales difference falls in the rang `r CI_lhs` and `r CI_rhs`, thus the sales difference is potentially like to be at lower end.

### 7.126 Two-sample t test vs matched pairs t
a): Two-sample treatment
```{r}
load("~/Documents/MSIT/3. Stats 431/R/Chapter 7/EX07-126PAIRED.rda")
pair = `EX07-126PAIRED`
sample_mean_1 = mean(pair$Group1)
sample_mean_2 = mean(pair$Group2)
n = length(pair$Group1)
variance_1 = var(pair$Group1)
variance_2 = var(pair$Group2)
degreeOfFreedom = min(length(pair$Group1),length(pair$Group2))-1
tscore = ((sample_mean_1-sample_mean_2)-0)/sqrt(variance_1/n+variance_2/n)
pvalue = 2*pt(tscore,df=degreeOfFreedom,lower.tail = TRUE)
```
sample_mean_group1 = `r sample_mean_1`  
sample_mean_group2 = `r sample_mean_2`  
sample_variance_group1 = `r variance_1`  
sample_variance_group2 = `r variance_2`
tscore = `r tscore` 
pvalue = `r pvalue`  

b): Pair-sample treatment
```{r}
n = length(pair[,1])
diff_sample = pair$Group1 - pair$Group2
diff_mean = mean(diff_sample)
diff_variance = var(diff_sample)
diff_std = sd(diff_sample)
diff_tscore = diff_mean/(diff_std/sqrt(n))
diff_pvalue = 2*pt(diff_tscore,df = n-1,lower.tail = TRUE)
```
Pair_sample_mean = `r diff_mean`  
Pair_sample_variance = `r diff_std^2`  
Pair_sample_tscore = `r diff_tscore`  
Pair_sample_pvalue = `r diff_pvalue`

c): Null Hypothese is there is no difference between 2 groups.Test-I has large pvalue which implies the null hypothese cannot be rejected, whereas, test-II has relativly small pvalue, we may consider to reject the null hypothese.  

### 7.128 Average service time
H0: chain's average is same: U1=U2
Ha: U1 != U2
```{r}
n1 = 308
n2 = 317
x_mean1=158.03
x_mean2=189.49
std1=33.8
std2=41.3
mean_diff = x_mean1 - x_mean2

tscore = mean_diff/sqrt(std1^2/n1 + std2^2/n2)
pvalue=2*pt(tscore,df = min(n1,n2)-1,lower.tail = TRUE)

t_star = qt(c(0.025,0.975),df=min(n1,n2))
    
CI_lhs = round(mean_diff + t_star[1]*sqrt(std1^2/n1 + std2^2/n2),0)
CI_rhs = round(mean_diff + t_star[2]*sqrt(std1^2/n1 + std2^2/n2),0)

```
a):  
pvalue = `r pvalue` is small, therefore we reject Null Hypothese, and in favor of alaternative hypothese: there exists the difference between 2 chains. 

b):  
95% CI is: (`r CI_lhs` , `r CI_rhs`) for the difference in average service time.  

c):  
We are 95% confident that they will encounter the difference in the CI calculated above.  

### 7.143 Do women perform better in school
We can assume group of female and male could have equal variance of GPA and IQ scores respectively.
```{r}
load("~/Documents/MSIT/3. Stats 431/R/Chapter 7/EX07-143GRADES.rda")
grades = `EX07-143GRADES`
grade_female = grades[which(grades$Gender=='1'),]
grade_male = grades[which(grades$Gender=='2'),]

hist(grade_female$GPA)
hist(grade_female$IQ)
hist(grade_male$GPA)
hist(grade_male$IQ)

male_GPA_mean = mean(grade_male$GPA)
male_IQ_mean = mean(grade_male$IQ)

female_GPA_mean = mean(grade_female$GPA)
female_IQ_mean = mean(grade_female$IQ)

n_female = length(grade_female[,1])
n_male = length(grade_male[,1])

female_GPA_std = sd(grade_female$GPA)
female_IQ_std = sd(grade_female$IQ)
male_GPA_std = sd(grade_male$GPA)
male_IQ_std = sd(grade_male$IQ)

pooled_GPA_std = sqrt(((n_female - 1)*female_GPA_std^2 + (n_male - 1)*male_GPA_std^2)/(n_female + n_male -2))
pooled_IQ_std = sqrt(((n_female - 1)*female_IQ_std^2 + (n_male - 1)*male_IQ_std^2)/(n_female + n_male -2))

pool_df = n_female+n_male -2

diff_GPA_mean = female_GPA_mean - male_GPA_mean
diff_GPA_se = pooled_GPA_std*sqrt(1/n_female + 1/n_male)
diff_IQ_mean = female_IQ_mean - male_IQ_mean
diff_IQ_se = pooled_IQ_std*sqrt(1/n_female + 1/n_male)


tscore_GPA = diff_GPA_mean/diff_GPA_se
pvalue_GPA = 2*pt(tscore_GPA,df = pool_df,lower.tail = FALSE)

tscore_IQ = diff_IQ_mean/diff_IQ_se
pvalue_IQ = 2*pt(tscore_IQ,df = pool_df,lower.tail = TRUE)

t_star_GPA = qt(c(0.025,0.975),df = pool_df,lower.tail = TRUE)
t_star_IQ = qt(c(0.025,0.975),df = pool_df,lower.tail = TRUE)

MOE_GPA = t_star_GPA * diff_GPA_se
MOE_IQ = t_star_IQ * diff_IQ_se

CI_GPA_diff_lhs = round(diff_GPA_mean + MOE_GPA[1],1) 
CI_GPA_diff_rhs = round(diff_GPA_mean + MOE_GPA[2],1)
  
CI_IQ_diff_lhs = round(diff_IQ_mean + MOE_IQ[1],1)
CI_IQ_diff_rhs = round(diff_IQ_mean + MOE_IQ[2],1)
```

a-1): pvalue_GPA_difference = `r pvalue_GPA` is large enough not to reject the hypothese: there is no difference between male and female on GPA  

a-2): pvalue_IQ_difference  = `r pvalue_IQ` is also large enough not to reject the hypothese: there is no difference between male and female on IQ  

b-1): CI of GPA_diff is (`r CI_GPA_diff_lhs` , `r CI_GPA_diff_rhs`)  

b-2): CI of IQ_diff is (`r CI_IQ_diff_lhs` , `r CI_IQ_diff_rhs`)  


### 8.29 P-hat and the normal distribution
```{r}
p_par = 0.4
n1=40
n2=80
dof1=n1-1
dof2=n2-1
pvalue=0.05

tscore_40=qt(c(0.025,0.975),df = dof1,lower.tail = TRUE)
p_hat_40 = round(tscore_40[2]*sqrt(p_par*(1-p_par)/n1)+p_par,2)

tscore_80 = qt(c(0.025,0.975),df = dof2,lower.tail = TRUE)
p_hat_80 = round(tscore_80[2]*sqrt(p_par*(1-p_par)/n2)+p_par,2)
```
a): sample proportion w/ sample size n = 40 is `r p_hat_40`  

b): sample proportion w/ sample size n = 80 is `r p_hat_80` 

c): Sketch t-bell shape distribution below:  
```{r}
curve(dt(x, 10), from = -3, to = 3, col = "orange",xlab = "quantile", ylab = "density", lwd = 2)
curve(dt(x, 500), from = -3, to = 3, col = "blue",xlab = "quantile", ylab = "density", add = TRUE,lwd = 2)
legend("topleft", legend = paste0("n = ", c(40, 80)),
       col = c("orange","blue"),
       lty = 1, lwd = 2)
```

### 8.36 Can we use the Z test
a): n=30, H0: p=0.3 >> np = 9 < 15  
This does NOT comply with Roburstness, shall not use Z-test  

b): n=60,H0: p=0.2  >> np = 12 < 15    
This does NOT comply with Roburstness, shall not use Z-test    

c): n=100, H0: p=0.12 >> np = 12 < 15  
This does NOT comply with Roburstness, shall not use Z-test    

d): n=150, H0: p=0.04 >> np = 6 < 15  
This does NOT comply with Roburstness, shall not use Z-test 

### 8.40 Is there interet in a new product
```{r}
MOE = 0.25
zstar = qnorm(0.95,0,1,lower.tail = TRUE)
sample_size = round(0.25*(zstar/MOE)^2,0)
```
For approaching 95% MOE be 0.25 or less, sample size needs to be at least `r sample_size`







