---
output:
  word_document: default
  html_document: default
---
## HW_4_Qian Cao
### Q1:4.57 Spell Checking software:
a):
```{r}
x=c(0,1,2,3,4)
y=c(0.1,0.3,0.3,0.2,0.1)
barplot(y,width = 1,xlab = "Value of X", ylab = "Probability",space = 0)
```
<br>

b):"At least one nonword error": P(X>=1) = 1-P(X=0) = 0.9  
c):X<=3 stands for "Less than 4 nonword error (exclusive)"   
P(X<=3) = 1-P(X=4) = 0.9  
P(X<3)  = 1-P(X=3 or X=4) = 1-(.2+.1) = 0.7  

### Q2:4.59 Uniform unmbers between 0 and 2:
a):
```{r}
uniform = table(runif(100,min = 0,max = 2))
barplot(uniform,xlab = "X random variable between 0 and 2", ylab = "Density")
```  
**b):**P(Y<=1.6) = (1.6-0)/2 = 0.8  
**c):**P(0.5<Y<1.7) = (1.7-0.5)/2 = 0.6  
**d):**P(Y>=.95) = (2-.95)/2 = 0.525

### Q3:4.62 Normal appromimation for a sample proportion:
a):mean=0.56, std=0.019
```{r}
p1=pnorm(.6,0.56,0.019)-pnorm(0.52,0.56,0.019)
```
p1 of P(0.52<=p<=.6) is `r round(p1,2)`
<br>

b):Considering the p>=0.72:
```{r}
p2=pnorm(.72,mean = .56,sd = 0.019,lower.tail = FALSE)
```
p2 of P(p>=072) is `r p2`  

### Q4:4.71 Find Variance and STD:
```{r}
X=c(-1,0,1,2)
P = c(0.3,0.2,0.3,0.2)
X2 = (X-mean(X))^2
variance=X2%*%P
std=sqrt(variance)
```
Variance = `r variance` and Standard Deviation = `r std`
<br>

### Q5:4.112 Education and Income:  
P(A): P(Prosperous) = 0.138    
P(B): P(Educated)=0.261   
P(A && B): P(Both event A and B happen) =0.082   
P(A || B)=P(A)+P(B)-P(A&&B) = `r 0.138+0.261-0.082`

### Q6:4.138 Sample surveys for sensitive issues:
P(head) = 0.5
P(plag)=0.3  
P(non_plag)=1-P(plag)=1-0.3=0.7  
**P(answer_no)** = P(head and non_plag) = P(head)P(non_plag)=0.35  

**If P(plag)=0.2, then P(non_plag)=0.8**: P(answer_no) = 0.5*0.8=0.4  

**If P(answer_no) = 0.39**: P(plagiarized) = 1- P(non_plagiatized) =1 - (0.39/0.5) = 0.22

### Q7:Spam filter:
P(Spam)=0.5  
P(Non_spam)=0.5  
i):  
Given P(d&p) = P(both discount and password)  
P(d&P|Spam)=0.2 * 0.4 = 0.08  
P(d&P|Non_spam) = 0.002 * 0.004  
**Therefore: the probablity of email with both "discount and password"is: ** 
P(Spam|d&p)=P(d&p|Spam)/[P(d&p|Spam)+P(d&p|Non_spam)] = 0.08/(0.08+(0.002*0.004)) = 0.9999
<br>

ii):  
P(p|Spam)=0.2  
P(p|Non_spam)=0.004  
**Therefore: the probablity of email with "password"is:**  
P(Spam|p)=0.2/(0.2+0.004)=0.98

### Q8: The Importance of Independence:
i)**Sample Space:**
S:{H,T,US,CA}
<br>

ii):CalculateP(A),P(B)andP(A&B)  
**P(A)**= P(H1)*P(US) or P(H1)*P(CA) = 0.5*(p+q)  
**P(B)**= P(H2)*P(US) or P(H2)*P(CA) = 0.5*(p+q)  
**P(A and B)** = 0.25*(p+q)^2  
A and B are independent  
<br>

iii): 


