---
output:
  word_document: default
  html_document: default
---
## HW_5_QianCao
###5.7 What population and sample:
a): Population = 153 English majors  
b): Sample = 30 students selected  
c): Statistic: Count of Yes from samples: 30 students  
d): Parameter: 1/3 for selecting statistics  
e): With SRS by 30 students from the population of 153 English mojor students,estimating the model's average of requirement if it is close to 1/3.

###5.38 Risk and insurance:
a): Fewer policy leads high variance which causes low consistancy, selling thousands of policy (increasing samples) helps on approaching model's mean = $500 more consistantly.  

```{r}
p = pnorm(600,500,10000/sqrt(50000),lower.tail = FALSE)
```
b): Approximate probability is `r round(p,4)*100`% that the average loss in a year will be greater $600  

###5.42 Investiment in two funds:  
a): R=0.7X+0.3Y  
```{r}
a=0.7
b=0.3
X_mean=0.1
Y_mean=0.09
X_std=0.15
Y_std=0.19
r=0.6
R_mean=a*X_mean+b*Y_mean
R_std =sqrt(a^2*X_std^2+b^2*Y_std^2+2*a*r*X_std*b*Y_std)
```
R_mean = `r R_mean`  
R_standard deviation = `r R_std`  


```{r}
n_year=20
P_0.05 = pnorm(0.05,R_mean,R_std/sqrt(n_year),lower.tail = TRUE)
```
b): Probablity of return less than 5% after 20 years = `r round(P_0.05*100,2)`% 


c-1): Return in the first year 12% return = 1000*(1+0.12) = `r 1000*(1+0.12)`  
c-2): Return in the second year 6% return = 1120*(1+0.06) = `r 1120*(1+0.06)`  
c-3): Return in both year 9% return : FV= 1000*(1+0.09)^2 = `r 1000*(1+0.09)^2`

###5.70 The ideal number of children:
a): Probability for sample proportion between 0.44 and 0.52
```{r}
p=0.48
n=1020
gallup_std=sqrt(p*(1-p)/n)
p_44=pnorm(0.44,p,gallup_std,lower.tail = TRUE)
p_52=pnorm(0.52,p,gallup_std,lower.tail = TRUE)
prob_in_btw = p_52-p_44
```
`r round(prob_in_btw*100,2)`% likely that sample proportion falls between 0.44 and 0.52

###5.97 A random walk:
```{r}
n=500
p_rhs=0.6
p_lhs=0.4
std_rhs=sqrt(n*(p_rhs*(1-p_rhs)))
std_lhs=sqrt(n*(p_lhs*(1-p_lhs)))
RW_mean=500*(p_rhs-p_lhs)
RW_std= sqrt(std_rhs^2+std_lhs^2)
p_200=pnorm(200,RW_mean,RW_std,lower.tail = FALSE)
p_200
RW_std
```
Probablity is approximate `r p_200` to be at leat right 200







