---
title: "HW8_QianCao"
output: word_document
---

### 8.63 Physical education requirement: 
a):  
Expanatory variables: number of institutions for public and private, number of institutions require PE 
Response variables: percent of institutions require PE  

b):Populations:  
0.97 and 0.40 are population proportion of institutions require PE in 1920 and today respectively  

c):Statistics:  
X_pv=60, n_pv=225, X_pb=101,n_pb=129  
p_pv_hat=60/225    
p_pb_hat=101/129  
D=p_pv_hat - p_pb_hat=-0.516    
SEd=sqrt(p_pv_hat(1-p_pv_hat)/n_pv + p_pb_hat(1-p_pb_hat)/n_pb)=0.047

d):  95%-CI calculation:  
```{r}
X_pv=60
n_pv=225
X_pb=101
n_pb=129  
p_pv_hat=X_pv/n_pv    
p_pb_hat=X_pb/n_pb
D=p_pv_hat - p_pb_hat
print (D)
SEd=sqrt(p_pv_hat*(1-p_pv_hat)/n_pv + p_pb_hat*(1-p_pb_hat)/n_pb)
print(SEd)
z_score=qnorm(c(0.025,0.975),0,1,lower.tail = TRUE)
print (z_score)
moe=z_score*SEd
print (moe)
CI_95 = D + moe
print (CI_95)
```
95% CI: `r CI_95`  

e): significance test to compare private and public: H0: p_pb = p_pv 
```{r}
p_hat = (X_pv+X_pb)/(n_pb+n_pv)
print (p_hat)
p_hat*(1-p_hat)

SEdp = sqrt(p_hat*(1-p_hat)*(1/n_pb+1/n_pv))
print (SEdp)
z_score2=D/SEdp
print (z_score2)
p_value = pnorm(z_score2,0,1,lower.tail = TRUE)*2
print (p_value)
```
p_value = `r p_value`, although we know the true P_VALUE is small

g): `r round(p_pv_hat,4)*100`% private schools require PE, and `r round(p_pb_hat,4)*100`% public schools require PE.  
Therefore the difference is statistically significant.  

### 8.75 Where do you get your news:
a):  
Sample_size=2342  
Count=1639  

b):  
Sample proportion = 1636/2342 = 70%  
Standard error=sqrt(0.7*0.3/2342) = 0.0095  

c):
```{r}
p_hat = 0.7
SEp = sqrt(0.7*0.3/2342)
print(SEp)
z_score3 = qnorm(c(0.025,0.975),0,1,lower.tail = TRUE)
moe=z_score3*SEp
print(moe)
CI_95= 0.7+moe
print(CI_95)
```
95% CI is: `r CI_95`  

d): No, this is a biased sampling, because we only did the survey from people who onw the laptop, and omit those not have laptop, which does not satisfies SRS (large-number) guidelines  

### 8.77 Use a confidence interval for comparison
```{r}
n5_10=194+861
n11_13=557+417
x5_10=861
x11_13=417
p_hat1=x5_10/n5_10
print (p_hat1)
p_hat2=x11_13/n5_10
print(p_hat2)
D = p_hat1 - p_hat2
SEd=sqrt(p_hat1* (1 - p_hat1)/n5_10 + p_hat2* (1- p_hat2)/ n11_13)
print(SEd)
z_score = qnorm(c(0.025,0.975),0,1,lower.tail = TRUE)
print(z_score)
moe = z_score*SEd
print(moe)
CI_95 = D+moe
print (CI_95)
```
With 95% confidence, we can say that the difference in the proportions is between `r CI_95`.  
Alternatively, we can report that difference in the proportion of 2 groups ages with calcium intake requirement in this population is `r round(D,4)*100`% with a 95% margin of error of `r round(moe[2],4)*100`%.

### 8.95 Calculating sample sizes for two-sample problem: 
```{r}
p_hat = 0.5
p_star = 0.5
z_score = z_score = qnorm(0.975,0,1,lower.tail = TRUE) 
moe = 0.055
n = 0.5*(z_score/0.055)**2
print (round(n,0))
```
Require a value of n: `r round(n,0)`.  
Fomula: (1/2)*(z_score/moe)**2 










